%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry%
    {General Secretary (2015 --- PRESENT), Joint Secretary (2014 --- 2015)} % Affiliation/role
    {Computer Society of India --- Jamia Millia Islamia Student's Chapter} % Organization/group
    {} % Location
    {2014 --- PRESENT} % Date(s)
    {%
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item{Was part of the team responsible for adding 300 new student registrations within a calendar year.}
        \item{Organised three technical workshops on Ethical Hacking and Network Security, Android Development and Python Programming.}
        \item{Organised a photography competition during annual fest AlgoRhythm and used the event as a front to get the fest photo coverage for free.}
        \item{Was part of the team that managed to draw sponsors worth Rs. 2 Lakhs.}
        \item{Proposed various marketing and network activities to raise awareness.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry%
    {Placement Co-Ordinator} % Affiliation/role
    {Department of Computer Engineering, Faculty of Engineering Technology} % Organization/group
    {} % Location
    {2015 --- 2016} % Date(s)
    {%
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {I am part of the team responsible for communicating with the prospective employers for placement opportunities.}
        \item {Mainly responsible for finding connections and contacts in the industry.}
        \item {Part of the team that organised and co-ordinated last year's batch's placement sessions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry%
    {Editorial Team} % Affiliation/role
    {FICTION --- Annual TechnoCultural Magazine of CSI-JMI} % Organization/group
    {} % Location
    {2013 --- 2015} % Date(s)
    {%
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item{Served as a member of the editorial team by editing, short-listing and contributing articles submitted to the magazine.}
        \item{Came up with online campaign ideas to improve the online presence of the magazine and the team.}
        \item{Served as the assistant designer for the magazine.}
        \item{Served as the lead graphic designer for the events and orientations related to the magazine.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry%
    {Goalkeeper} % Affiliation/role
    {Enginerring Faculty Soccer Team} % Organization/group
    {} % Location
    {2013 --- PRESENT} % Date(s)
    {%
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item{Participated in the intrafaculty and interfaculty tournaments each year and came 3rd twice.}
        \item{Participated in the national level BITS League 2014 but were knocked out in the round of 8.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry%
    {Member} % Affiliation/role
    {ANANT --- Dramatic's Society of Faculty of Engineering} % Organization/group
    {} % Location
    {2013 --- 2014} % Date(s)
    {%
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item{Took part in two plays organised on college premises in 2013.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

