%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Key Projects}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{projentries}

%---------------------------------------------------------
\projentry%
  {Visual Studio Code} % Project Title
  {TypeScript, Node.js} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{Frequent contributor to Microsoft's \textbf{VSCode, a code editor
            optimized for building and debugging modern web applications.}}
      \item{Named as a valuable contributor to the project in it's v1.5 August
            release.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Open Live Writer} % Project Title
  {C\#, .NET, HTML5, CSS, JavaScript} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{Primary \textbf{maintainer and developer of the product's webpage}
            at www.openlivewriter.org}
      \item{Frequent contributor to .NET Foundation’s blog authoring tool Open
            Live Writer.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Dockerised Development Environment} % Project Title
  {Bash, Docker} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems}
      \item{Docker containers that isolate a build system, dependencies and
            libraries and can be used as \textbf{background compilers to
            restrict system resources} and prevent clutterring the host OS.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Feed Notifier} % Project Title
  {Python} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{Used by the \textbf{Python Software Foundation} for managing it's
            GSoC students' blog schedule.}
      \item{A Python module that emails students and their mentors if they
            have not blogged according to the Google Summer of Code schedule.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Git Robot} % Project Title
  {Bash, C++} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A git wrapper that allows to run any arbitrary \textbf{git command
            on all git repositories within a directory tree.}}
      \item{Can check for outdated licences, ignore and attribute files,
            broken links in READMEs, repositories which are not in sync
            with upstream etc.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Linux Deployment Toolbox} % Project Title
  {Bash} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
    \item{Framework of sh compatible shell scripts that allows \textbf{mass
          deployment of a system configuration to all machines within an
          organisation.}}
    \end{projitems}
  }

%---------------------------------------------------------
\end{projentries}
