%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{projentries}

%---------------------------------------------------------
\projentry%
  {Visual Studio Code} % Project Title
  {TypeScript} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{Frequent contributor to Microsoft's code editing tool VSCode.}
      \item{Named as a valuable contributor to the project in it's v1.5 August
            release.}
      \item{Added 2 new features and fixed 2 issues in the last two months.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Open Live Writer} % Project Title
  {C\#, .NET} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{Frequent contributor to .NET Foundation’s blog authoring tool Open
            Live Writer.}
      \item{Primary maintainer and designer for the product's webpage at
            www.openlivewriter.org}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Feed Notifier} % Project Title
  {Python} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A Python module that emails students and their mentors if they
            have not blogged according to the Google Summer of Code schedule.}
      \item{Is used by the Python Software Foundation for managing it's GSoC
            students' blog schedule.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Linux Deployment Toolbox} % Project Title
  {Bash} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
    \item{Framework of sh compatible shell scripts that allows mass deployment
          of a system configuration to all machines within an organisation.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Git Robot} % Project Title
  {Bash, C++} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A git wrapper that allows to run any arbitrary git command on all
            git repositories within a directory tree.}
      \item{Adds commands to check for outdated licences, ignore and
            attribute files, broken links in readme files, list of forked
            repositories which are not in sync with upstream etc.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Mass Renamer} % Project Title
  {Golang} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A command line program that allows batch renaming of files using any
            text editor with support for undoing previous operations.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {CLI StackOverflow} % Project Title
  {C++} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{Command line interface to StackOverflow that allows searching for
            questions and users with filters based on tags and languages.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {XKCD Scraper} % Project Title
  {Python} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A Python program that downloads the web-comics from xkcd.com and
            overlays the image with the comic title and description.}
      \item{Also builds a text index of the downloaded comics which allows a
            keyword search on the comics.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Duplicate Song Detector} % Project Title
  {C\#, .NET} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A Windows GUI application which finds duplicate songs by comparing
            their acoustic charecteristics.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Exploratory Music Player} % Project Title
  {TypeScript} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A music player that clusters music according to it's acoustic
            features.}
      \item{Has a built in recommendation engine based on acoustic features.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {VSCode Universal Installer} % Project Title
  {Python} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A program that downloads, installs and configures Visual Studio
            Code according to the platform that it is running on.}
      \item{Was used as an alternative downloader for VSCode when no official
            packages and PPAs were available.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {NCurses Music Visualiser} % Project Title
  {C++} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A command line music visualsiser that runs within any terminal.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Cryptographic Hash Calculator and Verifier} % Project Title
  {C++} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A windows shell extension that adds hash calculation and
            verification abilities to Windows Explorer's context menu and to
            the Property sheet of any file.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Visual Studio Task Tags} % Project Title
  {C\#, .NET} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A Visual Studio extension that highlights all occurrences of
            configurable tokens (TODO, DEBUG etc.) and adds them to the Task
            List.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Traffic Monitor App} % Project Title
  {C\#, .NET, UWP} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A Universal Windows app that tracks driving times to various
            locations and alerts when it changes by more than 10 minutes due
            to traffic.}
    \end{projitems}
  }

%---------------------------------------------------------
\projentry%
  {Image Colorscheme Extractor} % Project Title
  {Bash, Python} % Language and Technology Used
  {} % Date(s)
  {%
    \begin{projitems} % Description(s) of tasks/responsibilities
      \item{A program to generate a colorscheme from a given image.}
      \item{Can generate schemes compatible with i3wm, Xresources or HTML.}
    \end{projitems}
  }

%---------------------------------------------------------
\end{projentries}
